Review of Assigned Readings

### 2018-01-04 paper/paper.tex

\subsection{Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria are measuring the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

@@

As can be seen, STATA calculates and presents various information criteria (AIC, HQIC, SBIC). The asterisk indicates the optimal lag lenght to use for the regression analysis. In this case all criteria suggest a lag length of 1.

\subsection{Regression Model}
After determining the optimal lag length the next step is to build the vector autoregression model (VAR model).\\
For this analysis, we use a basic unrestricted VAR model which consists of two endogenous variables, T\textsubscript t which repesents the variable {\itshape df\_nr\_of\_tweets} in our data set and B\textsubscript t which represents {\itshape df\_bpi\_closing\_price}. As defined in the previous section the selected otpimal time lag is 1. Given these information, the model equations can be written as follows:

>>>>

\subsection{Preparing for VAR: Lag-Specification}
To select the optimal number of lags to use for the VAR regression, we have to check for various information criteria. Information criteria measure the tradeoff between model fit and parsimony, giving the optimal number of lags to use (\cite[p.~27]{brandtwilliams2007}). The calculations of these criteria for our specific data set are shown in the following table.\\

@@

As can be seen, STATA calculates and presents various information criteria (AIC: Akaike Information Criterion, HQIC: Hannan–Quinn information criterion, SBIC: Schwarz-Bayesian Information Criterion). The asterisk indicates the optimal lag lenght to use for the regression analysis. In this case all criteria suggest a lag length of 1.

\subsection{VAR Regression Model}
After determining the optimal lag length the next step is to build the vector autoregression model (VAR model).\\
For this analysis, we use a basic unrestricted VAR model which consists of two endogenous variables, T\textsubscript t which repesents the variable {\itshape df\_nr\_of\_tweets} in our data set and B\textsubscript t which represents {\itshape df\_bpi\_closing\_price}. As defined in the previous section the selected otpimal time lag is 1. Given these information, the model equations can be written as follows:
